Planar Maximal Covering with Ellipses

### 2019-04-30 quali/quali.presentation/slides.tex
WIP

\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
\usepackage{algorithmicx}
\usepackage{algorithm}
%\usepgfplotslibrary{external}
%\tikzexternalize

@@

\title[Qualificação de Mestrado]{Planar Maximal Covering with Ellipses}
\author[Tedeschi, D. F.]{Danilo F. Tedeschi}
\institute[ICMC]{Instituto de Ciências Matemáticas e Computação}
\date{\today}

@@

\begin{frame}
 \maketitle
\end{frame}

@@

		\caption{The elliptical and euclidean norms.}
		\input{figures/elliptical.and.euclidean.norms.tex}
		%\fautor
		\label{fig:3ellipses_intersect}
	\end{figure}
\end{frame}

@@

		\caption{An instance of $MCD(\Pp,1)$.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
      \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
		%\fautor
		\label{fig:mcd_instance}
	\end{figure}
\end{frame}

@@

		\caption{An instance of Maximum Weight Clique Problem.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
		%\fautor
		\label{fig:max_wieght_clique}
	\end{figure}
\end{frame}

@@

		\caption{Three disks and their intersection points.}
		\input{figures/img2.tex}
		%\fautor
		\label{fig:3disks_intersect}
	\end{figure}
\end{frame}

@@

	\caption{The intersections list of a disk with three other disks.}
	\input{figures/fig:array_disks.tex}
%	\fautor
	\label{fig:array_disks}
\end{figure}
\end{frame}

@@

	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
	\input{figures/mcd_sim.tex}
	%	\fautor
	%\label{fig:array_disks}
\end{figure}
\end{frame}

@@

\begin{block}{Multiple disks}
	For every disk, try every possible assignment that the traversal goes through. \cite{cabello:2006} proposed a $\bigO(n^{2m-1})$ algorithm.
\end{block}

@@

\begin{frame}{Maximal Covering by Ellipses}
	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by

@@

\begin{frame}{Maximal Covering by Ellipses}
\begin{figure}[H]
	\centering

	\caption{Intersection points of $E_1$ with $E_2$ and $E_3$ along with opening and closing angles indicators.}
	\input{figures/3ellipses_with_gammas.tex}
	%	\fautor
	\label{fig:3ellipses_with_gammas}
\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item $\E$ is a set of $m$ ellipses
		\item \cite{andreta,canbolat} are the works found on the problem which the ellipses have costs
		\item \cite{andreta} also developed a method for the non-axis-parallel case
	\end{itemize}
\end{frame}

\begin{frame}{Maximal Covering by Ellipses}{$m$ ellipses}
	\begin{algorithm}[H]
	%	\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
		%\KwIn{alskdjf}

		\begin{algorithmic}[1]
			\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and the shape parameters $(a, b)$ of an ellipse.}
			%\Ensure{A collection of subsets of $\Pp$ that the ellipse is able to cover.}

			%\item[]
			%\Procedure{$MCE_1$}{$\Pp, a, b$}
			%\State $Z \gets \{\}$ \Comment{A collection of subsets of $\Pp$, each being a possible coverage.}

			%\ForAll{$p_i \in \Pp$}
			%\State Let $E_i$ be the ellipse with center at $p_i$ and parameters $(a,b)$

			%\State Let $I_i$ be the set of ellipses that intersect with $E_i$

			%\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $E_i$}

			%\State $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$ %\Comment{The multiset of intersection angles with $E_i$.}

			%\ForAll{$j \in I_i$}
			%\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			%\EndFor

			%\State $Z \gets Z \cup \{\{p_i\}\}$
			%\State $Cov \gets \{p_i\}$ \Comment{The set of active disks.}

			%\For{$cnt=1..2$} \Comment{Do it twice.}
			%\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
			%\State Let $p_a$ be the point represented by the ellipse that intersects $E_i$ at angle $a$. 
			%\If{$a$ is a starting angle}
			%\State $Cov \gets Cov \cup \{p_a\}$
			%\Else
			%\State $Cov \gets Cov \setminus \{p_a\}$
			%\EndIf
			%\State $Z \gets Z \cup \{Cov\}$
			%\EndFor
			%\EndFor
			%\EndFor

			%\State \Return $Z$
			%\EndProcedure

@@

\section{Trabalhos Futuros}

\begin{frame}{Trabalhos Futuros}

@@

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=1.4}
\usepackage{algorithm2e}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{caption}
\newcommand{\source}[1]{\caption*{Source: {#1}} }

%\usepgfplotslibrary{external}
%\tikzexternalize

@@

\title[Qualificação de Mestrado]{Planar Maximal Covering with Ellipses}
\author[Tedeschi, D. F.]{Danilo F. Tedeschi\\ \small Orientadora: Dra. Marina Andretta}

\institute[ICMC]{Instituto de Ciências Matemáticas e Computação}
\date{\today}

@@

\begin{frame}
 \maketitle

\centering Thanks to CAPES
\end{frame}

@@

		\caption{The elliptical and euclidean norms}
		\input{figures/elliptical.and.euclidean.norms.tex}
		\source{Elaborated by the author.}
		\label{fig:3ellipses_intersect}

	\end{figure}
\end{frame}

@@

		\caption{An instance of $MCD(\Pp,1)$.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
      \center{\includegraphics[width=.7\textwidth]{figures/mcd_instance.png}}
		\source{Elaborated by the author.}
		\label{fig:mcd_instance}
	\end{figure}
\end{frame}

@@

		\caption{An instance of Maximum Weight Clique Problem.}
		%\input{figures/elliptical.and.euclidean.norms.tex}
		\center{\includegraphics[width=.7\textwidth]{figures/mwc_instance.png}}
		\source{Elaborated by the author.}
		\label{fig:max_wieght_clique}
	\end{figure}
\end{frame}

@@

		\caption{Three disks and their intersection points.}
		\input{figures/img2.tex}
		\source{Elaborated by the author.}
		\label{fig:3disks_intersect}
	\end{figure}
\end{frame}

@@

	\caption{The intersections list of a disk with three other disks.}
	\input{figures/fig:array_disks.tex}
	\source{Elaborated by the author.}
	\label{fig:array_disks}
\end{figure}
\end{frame}

@@

	\caption{A traversal for $D_1$ with green disks representing the active set and red signs representing the current angle being visited (some are omitted).}
	\input{figures/mcd_sim.tex}
		\source{Elaborated by the author.}
	%\label{fig:array_disks}
\end{figure}
\end{frame}

@@

\begin{frame}{Maximum Weight Clique Problem}{Multiple disks}
	\begin{itemize}
		\item In \cite{cabello:2006} a $\bigO(n^{2m-1})$ algorithm was proposed. Also a $(1-\epsilon)-$approximation that runs in $\bigO(n\log{n})$ was introduced.

		\item In \cite{zhou} a heuristic method using an algorithm called mean-shift was developed. The mean-shift algorithm converges to a local density maxima of any probability distribution and it is used to find a smaller candidate list of centers for the disks.
	\end{itemize}

@@

\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by

@@

\begin{frame}{Maximal Covering by Ellipses}{One ellipse}
\begin{figure}[H]
	\centering

	\caption{Intersection points of $E_1$ with $E_2$ and $E_3$ along with opening and closing angles indicators.}
	\input{figures/3ellipses_with_gammas.tex}
	\source{Elaborated by the author.}
	\label{fig:3ellipses_with_gammas}
\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item $\E$ is a set of $m$ ellipses
		\item \cite{canbolat} is the very first study on the problem. Slow exact method, a heuristic one was proposed.
		\item \cite{andreta} proposed a method that breaks the problem into smaller optimization ones. Also, they developed a method for the non-axis-parallel case.
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Maximal Covering by Ellipses}{Pre-processing that finds every possible coverage for ellipse $E_i$}
	\begin{algorithm}[H]
		%\caption{Algorithm for $MCE(\Pp, a, b)$ with unit weights}\label{algoritmo:mce1}
		\begin{algorithmic}[1]
			\STATE $A \gets \bigcup_{j \in I_i} \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
			\STATE $Z \gets \{\}$

			\FOR{$cnt=1..2$} 
			\FOR{$a \in A$}
			\STATE Let $p_a$ be the point that intersects $E_i$ at angle $a$. 
			\IF{$a$ is a starting angle}
			\STATE $Cov \gets Cov \cup \{p_a\}$
			\ELSE
			\STATE $Cov \gets Cov \setminus \{p_a\}$
			\ENDIF
			\STATE $Z \gets Z \cup \{Cov\}$
			\ENDFOR
			\ENDFOR

@@

\begin{frame}{Maximal Covering by Ellipses}

	\begin{itemize}
		\item The algorithm for $m$ ellipses tries every possible assignment of coverage for every one of the ellipses
		\item Run-time complexity of $\bigO(n^2)^m = \bigO(n^{2m})$

		\item Simpler than the $m$ disks algorithm proposed by \cite{cabello:2006}. Achieves a similar complexity ($\bigO(n^{2m-1})$).

		\item Small improvements can be made in the pre-processing exhibited earlier in oder to reduce the size of the search space:
		\begin{itemize}
			\item Non-maximal coverage sets.
			\item Ellipses that are too distant do not need to be checked.
		\end{itemize}

		\item The unit-weight assumption can be easily dropped
	\end{itemize}

@@

\section{Future Work}

\begin{frame}{Future Work}
	Primary goals:
\begin{itemize}
	\item Study the $(1-\epsilon)$-approximation method for the planar covering with disks in \cite{cabello:2006} and develop an adapted version of the algorithm for ellipses with the same time complexity of $\bigO(n\log{n})$.

	\item Develop an exact method for the version of the problem introduced in \cite{andreta} where the ellipses can be freely rotated.
\end{itemize}
\end{frame}

\begin{frame}{Future Work}

	Secondary goals:
	\begin{itemize}

	\item Develop a probabilistic approximation algorithm based on \cite{aronov:2008} which proposed a Monte Carlo approximation for the problem of finding the deepest point in a arrangement of regions. The method runs in $\bigO(n\epsilon^2\log{n})$ and can be applied to solve the case with one ellipse. The case with more than one ellipse is left as a challenge for us for the next steps of our research.

	\item In \cite{zhou}, the task of finding every center candidate, after eliminating all the non-essential ones, is done in $\bigO(n^5)$ run-time complexity. We want to generalize this for the elliptical distance function and achieve a better run-time complexity. We also intend to use the mean-shift algorithm to try to develop a greedy version for the ellipses version.

		\end{itemize}
\end{frame}
